---
title: "Activity Ten - Lab10"
author: "Taehoon Ha"
date: 11/13/2018
output: 
    github_document:
        toc: true
        toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

### Question 1
Generate Generate 1000 uniform pseudorandom variates using the `runif()` function.
+ compute average and variance
+ compare your results with true mean and variance
```{r}
set.seed(1)
dat <- runif(1000)
mean(dat)
var(dat)
```

### Question 2
Use the `round()` function together with `runif()` to generate 1000 pseudo-random integers which take values from 1 through 10. Use the `table()` function to check whether the observed frequencies for each value are close to what you expect.
```{r}
set.seed(1)
dat2 <- runif(1000, min = 0.5, max = 10.5) %>% round
table(dat2)
```

<br>

### Question 3
Use sample() function to generate 1000 pseudo-random integers which take values from 1 through 10.
Use the `table()` function to check whether the observed frequencies for each value are close to what you expect.
```{r}
set.seed(1)
dat3 <- sample(1:10, 1000, replace = T)
table(dat3)
```

<br>

### Question 4
Simulate 10000 binomial pseudo-random numbers with parameters 10 and 0.4. Let X be a Binomial(10, 0.4) random variable. Use the simulated numbers to estimate the following quantities:

+ Pr($X \le 3$)
+ Pr($X = 3$)

```{r}
x <- rbinom(1000000, 10, 0.4)
table(x)

length(x[x<=3]) / length(x)
length(x[x==3]) / length(x) 

pbinom(3, 10, 0.4) %>% round(3)
dbinom(3, 10, 0.4) %>% round(3)

table(x)
```


